Examples of Customization

### 2016-12-05 README.Rmd
Update README to match vignette

The first element of the returned object can be used to explore the behavior of individual simulations. For example, to look at the relative risk point estimate and 95% confidence interval from each of the 100 simulations, as well as which 95% confidence intervals include the true relative risk using the following call:

```{r fig.width = 4, fig.height = 5, fig.align = "center"}
ex_sim[[1]] %>%
  arrange(Estimate) %>%
  mutate(index = 1:n(),
         rr = exp(Estimate),
         lower_rr = exp(lower_ci),
         upper_rr = exp(upper_ci),
         includes_true = lower_rr < 1.10 & 1.10 < upper_rr) %>%
  ggplot(aes(x = index, y = rr, color = includes_true)) + 
  coord_flip() + 
  geom_point() + 
  geom_errorbar(aes(ymin = lower_rr, ymax = upper_rr)) + 
  geom_hline(yintercept = 1.10, linetype = 2) + 
  scale_color_manual(values = c("red", "darkgray")) +
  theme(legend.position="none",
        panel.background = element_rect(fill='white', colour='white')) + 
  ylab("Relative risk") +
  scale_x_discrete(breaks = NULL) + xlab("") 
```

@@

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
x_cont %>% 
  mutate(Weekday = lubridate::wday(date), 
         Month = lubridate::month(date, label = TRUE),
         Year = lubridate::year(date),
         Exposure = x) %>% 
  group_by(Year, Month) %>%
  dplyr::mutate(saturday = lag(Weekday) == 7,
                saturday = ifelse(is.na(saturday), 0, saturday),
                Week = 1 + cumsum(saturday)) %>%
  ungroup() %>%
  ggplot(aes(x = Weekday, y = Week, fill = Exposure)) + 
   geom_tile(colour = "white") + 
   facet_grid(Year ~ Month, scales = "free") + 
  scale_fill_gradientn(colours = viridis(256)) + 
  scale_y_reverse() + theme_void()
```

@@

```{r}
x_bin <- sim_exposure(n = 1000, central = 0.1,
                      exposure_type = "binary")
x_bin %>% slice(1:5)
```
```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
x_bin %>% 
  mutate(Weekday = lubridate::wday(date), 
         Month = lubridate::month(date, label = TRUE),
         Year = lubridate::year(date),
         Exposure = factor(x, levels = c(0, 1), 
                    labels = c("Not exposed", "Exposed"))) %>% 
  group_by(Year, Month) %>%
  dplyr::mutate(saturday = lag(Weekday) == 7,
                saturday = ifelse(is.na(saturday), 0, saturday),
                Week = 1 + cumsum(saturday)) %>%
  ungroup() %>%
  ggplot(aes(x = Weekday, y = Week, fill = Exposure)) + 
   geom_tile(colour = "white") + 
   facet_grid(Year ~ Month, scales = "free") + 
  scale_fill_manual(values = c("#414487FF", "#7AD151FF")) + 
  scale_y_reverse() + theme_void()
```

@@

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
testexp %>% 
  mutate(Weekday = lubridate::wday(date), 
         Month = lubridate::month(date, label = TRUE),
         Year = lubridate::year(date),
         Exposure = x) %>% 
  group_by(Year, Month) %>%
  dplyr::mutate(saturday = lag(Weekday) == 7,
                saturday = ifelse(is.na(saturday), 0, saturday),
                Week = 1 + cumsum(saturday)) %>%
  ungroup() %>%
  ggplot(aes(x = Weekday, y = Week, fill = Exposure)) + 
   geom_tile(colour = "white") + 
   facet_grid(Year ~ Month, scales = "free") + 
  scale_fill_gradientn(colours = viridis(256)) + 
  scale_y_reverse() + theme_void()
```

@@

```{r, fig.width = 5, fig.height = 3, fig.align = "center"}
smallamp <- sim_exposure(n=1000, central = 50, sd = 5, trend = "cos1linear",
                        amp = .2, exposure_type = "continuous")
qplot(smallamp$date, smallamp$x)+geom_point()+coord_cartesian(ylim = c(0,110))+labs(title = "Cos1linear exposure with smaller amplitude", x="Date", y="Exposure") + theme_bw()
```

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
smallamp %>% 
  mutate(Weekday = lubridate::wday(date), 
         Month = lubridate::month(date, label = TRUE),
         Year = lubridate::year(date),
         Exposure = x) %>% 
  group_by(Year, Month) %>%
  dplyr::mutate(saturday = lag(Weekday) == 7,
                saturday = ifelse(is.na(saturday), 0, saturday),
                Week = 1 + cumsum(saturday)) %>%
  ungroup() %>%
  ggplot(aes(x = Weekday, y = Week, fill = Exposure)) + 
   geom_tile(colour = "white") + 
   facet_grid(Year ~ Month, scales = "free") + 
  scale_fill_gradientn(colours = viridis(256)) + 
  scale_y_reverse() + theme_void()
```

@@

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
testbin %>% 
  mutate(Weekday = lubridate::wday(date), 
         Month = lubridate::month(date, label = TRUE),
         Year = lubridate::year(date),
         Exposure = factor(x, levels = c(0, 1), 
                    labels = c("Not exposed", "Exposed"))) %>% 
  group_by(Year, Month) %>%
  dplyr::mutate(saturday = lag(Weekday) == 7,
                saturday = ifelse(is.na(saturday), 0, saturday),
                Week = 1 + cumsum(saturday)) %>%
  ungroup() %>%
  ggplot(aes(x = Weekday, y = Week, fill = Exposure)) + 
   geom_tile(colour = "white") + 
   facet_grid(Year ~ Month, scales = "free") + 
  scale_fill_manual(values = c("#414487FF", "#7AD151FF")) + 
  scale_y_reverse() + theme_void()
```

@@

```{r fig.width = 5, fig.height = 3, fig.align = "center"}
testexp2 <- sim_exposure(n=1000, central = 100, sd = 10, trend = "cos1", exposure_type = "continuous")
testout <- sim_outcome(exposure = testexp2, average_outcome = 22, trend = "linear", rr = 1.01)
qplot(testout$date, testout$outcome)+geom_point()+labs(title = "Health outcomes with a linear trend", x="Date", y="Outcome") + theme_bw()
```

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
testout %>% 
  mutate(Weekday = lubridate::wday(date), 
         Month = lubridate::month(date, label = TRUE),
         Year = lubridate::year(date),
         Exposure = outcome) %>% 
  group_by(Year, Month) %>%
  dplyr::mutate(saturday = lag(Weekday) == 7,
                saturday = ifelse(is.na(saturday), 0, saturday),
                Week = 1 + cumsum(saturday)) %>%
  ungroup() %>%
  ggplot(aes(x = Weekday, y = Week, fill = Exposure)) + 
   geom_tile(colour = "white") + 
   facet_grid(Year ~ Month, scales = "free") + 
  scale_fill_gradientn(colours = viridis(256)) + 
  scale_y_reverse() + theme_void()
```

@@

```{r}
sims <- create_sims(n_reps=10, n=100, central = 100, sd = 10,
             exposure_type="continuous", exposure_trend = "cos1",
             exposure_amp = .6, average_outcome = 22,
             outcome_trend = "no trend", outcome_amp = .6, rr = 1.01)
fits <- fit_mods(outcome = sims, model = "spline", df_year = 7)
fits
```

@@

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
customexp %>% 
  mutate(Weekday = lubridate::wday(date), 
         Month = lubridate::month(date, label = TRUE),
         Year = lubridate::year(date),
         Exposure = x) %>% 
  group_by(Year, Month) %>%
  dplyr::mutate(saturday = lag(Weekday) == 7,
                saturday = ifelse(is.na(saturday), 0, saturday),
                Week = 1 + cumsum(saturday)) %>%
  ungroup() %>%
  ggplot(aes(x = Weekday, y = Week, fill = Exposure)) + 
   geom_tile(colour = "white") + 
   facet_grid(Year ~ Month, scales = "free") + 
  scale_fill_gradientn(colours = viridis(256)) + 
  scale_y_reverse() + theme_void()
```

>>>>

The first element of the returned object can be used to explore the behavior of individual simulations. For example, to look at the relative risk point estimate and 95% confidence interval from each of the 100 simulations, as well as which 95% confidence intervals include the true relative risk using the `coverage_plot` function that comes with the package:

```{r fig.width = 4, fig.height = 5, fig.align = "center"}
coverage_plot(ex_sim[[1]], true_param = 1.10)
```

@@

You can plot a calendar plot of this simulated exposure time series using the `calendar_plot` function that comes with the package:

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
calendar_plot(x_cont, type = "continuous")
```

@@

```{r}
x_bin <- sim_exposure(n = 1000, central = 0.1,
                      exposure_type = "binary")
x_bin %>% slice(1:5)
```

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
calendar_plot(x_bin, type = "discrete", labels = c("Not exposed", "Exposed"))
```

@@

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
calendar_plot(testexp, type = "continuous")
```

@@

```{r, fig.width = 5, fig.height = 3, fig.align = "center"}
smallamp <- sim_exposure(n=1000, central = 50, sd = 5, trend = "cos1linear",
                        amp = .2, exposure_type = "continuous")
qplot(smallamp$date, smallamp$x) +
  geom_point() + coord_cartesian(ylim = c(0,110)) +
  labs(title = "Cos1linear exposure with smaller amplitude", x="Date", y="Exposure") + theme_bw()
```

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
calendar_plot(smallamp, type = "continuous")
```

@@

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
calendar_plot(testbin, type = "discrete", labels = c("Not exposed", "Exposed"))
```

@@

```{r fig.width = 5, fig.height = 3, fig.align = "center"}
testexp2 <- sim_exposure(n=1000, central = 100, sd = 10, trend = "cos1", exposure_type = "continuous")
testout <- sim_outcome(exposure = testexp2, average_outcome = 22, trend = "linear", rr = 1.01)
qplot(testout$date, testout$outcome) + geom_point() +
  labs(title = "Health outcomes with a linear trend", x="Date", y="Outcome") + theme_bw()
```

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
calendar_plot(testout %>% select(date, outcome), type = "continuous")
```

@@

```{r}
sims <- create_sims(n_reps = 10, n = 100, central = 100, sd = 10,
             exposure_type="continuous", exposure_trend = "cos1",
             exposure_amp = .6, average_outcome = 22,
             outcome_trend = "no trend", outcome_amp = .6, rr = 1.01)
fits <- fit_mods(outcome = sims, model = "spline", df_year = 7)
fits
```

@@

```{r fig.align = "center", fig.width = 8, fig.height = 2.5}
calendar_plot(customexp, type = "continuous")
```
